\begin{abstract}
This research proposes an innovative solution to improve automated Forex trading systems using the Deep Deterministic Policy Gradient algorithm within a Deep Reinforcement Learning framework. Despite advances in Deep Reinforcement Learning applications in financial markets, integrating Deep Deterministic Policy Gradient with Recurrent Neural Networks, particularly Long-Short Term Memory networks, remains underexplored in Forex trading. This study addresses this gap by developing a trading system that incorporates the Deep Deterministic Policy Gradient algorithm, enriched with Long-Short Term Memory networks to handle sequential data and temporal dependencies. The proposed system integrates with the cTrader platform, enabling online learning and real-time strategy execution through a client-server architecture. The evaluation framework includes extensive backtesting using historical data, with performance evaluated against baseline strategies through metrics such as Net Profit, Sharpe Ratio, and Maximum Drawdown. The robustness of the system will be improved by implementing advanced feature engineering, normalisation, regularisation, and adaptive learning techniques. This research aims to deliver a robust and adaptive solution for automated Forex trading, with the potential for superior risk-adjusted returns and significant advancements over existing methodologies. Spanning from June 2024 to February 2025, this project seeks to fill existing research gaps and establish a new benchmark in automated Forex trading through the innovative application of Deep Reinforcement Learning technologies.
\keywords{Forex Trading, Neural Networks, Deep Reinforcement Learning, Deep Deterministic Policy Gradient}
\clearpage
\end{abstract}
 